---
title: "Oxfordshire Demo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{IOW}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MinorRoadTraffic)
```

Download raw data

Fix for internet problems `assign("has_internet_via_proxy", TRUE, environment(curl::has_internet))`

```{r download}
osm_raw = osmextract::oe_get("Oxfordshire", 
                             extra_tags = c("ref","highway","junction","maxspeed"))

aadt = download_dft_aadt()
```

We also need some zonal statistics, here we will use data from the [Place-Based Carbon Calculator](https://www.carbon.place) and employment statistics from [NOMIS](https://www.nomisweb.co.uk)

```{r read_lsoa}

zones = download_lsoa()
pbcc = download_pbcc()

zones = zones[,c("LSOA11CD")]
pbcc = pbcc[,c("LSOA11","pop_2018","cars_percap_2018")]

zones = dplyr::left_join(zones, pbcc, by = c("LSOA11CD" = "LSOA11"))

```


Subset AADT data to Oxfordshire in 2018

```{r subset}
aadt = aadt[aadt$Year == 2018,]
aadt = aadt[aadt$Local_authority_name == "Oxfordshire",]
aadt$traffic_flow = aadt$All_motor_vehicles
```

Make a bounding polygon for the study area, and crop the OSM data to that area.

```{r clip}
bounds = make_convex_hull(aadt, 5000)
osm_clean = extract_from_osm(osm_raw, bounds)
network = osm_clean$network
junctions = osm_clean$junctions
rm(osm_clean, osm_raw)
```

And we will subset our zone statistics

```{r clip_stats}
zones = zones[bounds,]
```

In the OSM roads don't always have a ref value (e.g. A123), so lets clean that up.

```{r clean_ref}
network = osm_fill_ref(network)
```
Before joining the AADT data to the road network, lets check that the IDs match

```{r check_ref}
summary(unique(aadt$Road_name[aadt$Road_type == "Major"]) %in% unique(network$ref))
```
In  this case there are no missing IDs, sometimes a manual fix to the data is needed.

```{r assign_aadt}
aadt_assign = assign_aadt_major(network, junctions, aadt, bounds)
network = aadt_assign$network
junctions_major_minor = aadt_assign$junctions_major_minor
```
Lets make a plot of our progress. Here we can see the minor roads in grey and the major roads coloured by their AADT. Junctions between major and minor roads are highlighted in blue. These junctions are important as they are the places traffic can leave the major road network and join the minor road network.

```{r plot1}
library(tmap)
tm_shape(network) +
  tm_lines(lwd = 2, col = "traffic_flow") +
  tm_shape(junctions_major_minor) +
  tm_dots(col = "blue", size = 0.08)
```
Now lets analyse the minor road network


```{r minor_distances}
network = minor_roads_distance(network, junctions_major_minor)
```
Calculate the centrality of minor roads. Centrality is a measure of the importance of a road, with higher centrality suggestion it is a road that connects different places together. Note calculating centrality on large networks is time-consuming, so this function breaks the network into zones based on the major road network. 

```{r minor_centrality}
network = road_centrality(network)
```

Lets check the results.

```{r plot1}
tm_shape(network) +
  tm_lines(lwd = 2, col = "std_centrality")
```

Calculate road density

```{r density}
density = road_density(network, zones)
network = density$network
zones = density$zones

```
```{r plot2}
tm_shape(network) +
  tm_lines(lwd = 2, col = "road_density")
```

We can join on other variables from the zones data

```{r plot2}
network = sf::st_join(network, zones[,c("pop_2018","cars_percap_2018")], largest = TRUE)
```


Now we can assign our minor road traffic data and attempt to model the missing data

```{r assign_minor_aadt}
aadt_minor <- st_buffer(aadt[aadt$Road_type == "Minor",], 6)
aadt_minor <- aadt_minor[,"traffic_flow"]
names(aadt_minor)[1] = "traffic_flow_minor"
network <- st_join(network, aadt_minor)
summary(is.na(network$traffic_flow_minor))
```
Build a simple linear model

```{r simple_model}
m1 = lm(traffic_flow_minor ~ log(major_flow) + log(nearest_junc_dist) + log(std_centrality) +
          log(road_density) + log(pop_2018) + log(cars_percap_2018),
        data = network)
summary(m1)
```

```{r glm_plot}
plot(network$traffic_flow_minor[!is.na(network$traffic_flow_minor)], predict(m1),
     xlab = "Obsereved AADT",
     ylab = "Predicted AADT")
abline(0,1)
```
Now try a Geographically Weighted Regression

```{r, GWR model}
library(GWmodel)

#GWR uses points not lines
cents = st_centroid(network)
cents$log_std_centrality = log(cents$std_centrality)
cents$log_nearest_junc_dist = log(cents$nearest_junc_dist)
cents$log_major_flow = log(cents$major_flow)

cents_test = cents[!is.na(cents$traffic_flow_minor),]

DM = gw.dist(dp.locat = st_coordinates(cents_test))

# Define Equation
eq = traffic_flow_minor ~ log_std_centrality + log_nearest_junc_dist + log_major_flow +
  pop_2018 + cars_percap_2018

# Determine the adaptive bandwidth
abw <- bw.ggwr(eq,
               data = as(cents_test, "Spatial"),
               family = "poisson",
               approach = "AICc",
               kernel = "bisquare", 
               adaptive = TRUE,
               dMat = DM)

# Fit GWPR
gwpr4 <- ggwr.basic(eq, 
                    data = as(cents_test, "Spatial"), 
                    family = "poisson",
                    bw = abw,
                    kernel = "gaussian",
                    adaptive = TRUE,
                    dMat = DM)

gwpr4


```


```{r, gwr_plot}
plot(cents_test$traffic_flow_minor,gwpr4$glms$fitted.values,
     xlab = "Obsereved AADT",
     ylab = "Predicted AADT")
abline(0,1)
```

Now predict traffic for all roads

```{r, GWR model}
cents_predict = cents[is.na(cents$traffic_flow_minor),]
#cents_predict = cents_predict[is.na(cents_predict$traffic_flow),]
cents_test = cents[!is.na(cents$traffic_flow_minor),]
DM1 = gw.dist(dp.locat = st_coordinates(cents_test), rp.locat = st_coordinates(cents_predict))
DM2 = gw.dist(dp.locat = st_coordinates(cents_test))

# Fit GWPR
pred = gwr.predict(eq, 
                    data=as(cents_test, "Spatial"),
                    predictdata = as(cents_predict, "Spatial"),
                    bw = abw,
                    kernel = "gaussian",
                    adaptive = TRUE,
                    dMat1 = DM1,
                    dMat2 = DM2)
prediction = st_as_sf(pred$SDF) 

```

```{r plot5}
tm_shape(prediction) +
  tm_dots(col = "prediction")
```

Join back onto network


